Data Preparation, Integration and Cleaning

### 2018-05-29 scripts/3_data_prep.Rmd
Update functions in data_prep

   setCleanCount()

@@

  countCleaning('time')

@@

   # Count Cleaning
   countCleaning('property_type')

@@

  # Count cleaning
  countCleaning('listing_type')

@@

  # Count Data Cleaning
  countCleaning('bedrooms')

@@

   # Count cleaning
   countCleaning('baths')

@@

 # Count Cleaning

  countCleaning('bedbath')

@@

  # Count Cleaning
  countCleaning('hostpolicy')

@@

   # Count Cleaning
   countCleaning('location')

@@

   # Count Cleaning
   countCleaning('rates_rents')

@@

   save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
        col_df, clean_count, core_suburbs,
        file=paste0(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData')))

>>>>

   clean_obj <- setCleanCount()

@@

  clean_obj <- countCleaning(clean_obj, 'time')

@@

   # Count 
   clean_obj <- countCleaning(clean_obj, 'property_type')

@@

  # Count cleaning
  clean_obj <- countCleaning(clean_obj, 'listing_type')

@@

  # Count Data Cleaning
    clean_obj <- countCleaning(clean_obj, 'bedrooms')

@@

   # Count cleaning
  clean_obj <- countCleaning(clean_obj, 'baths')

@@

 # Count Cleaning
  clean_obj <- countCleaning(clean_obj, 'bedbath')

@@

  # Count Cleaning
  clean_obj <- countCleaning(clean_obj, 'hostpolicy')

@@

   # Count Cleaning
  clean_obj <- countCleaning(clean_obj, 'location')

@@

   # Count Cleaning
  clean_obj <- countCleaning(clean_obj, 'rates_rents')

@@

   save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
        col_df, clean_obj, core_suburbs,
        file=paste0(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData')))
